Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-05-04 PAPER/main.tex
major changes

\documentclass[oribibl]{llncs}

\input{includes/preamble.tex}

@@

\title{Heuristics for the Score-Constrained Strip-Packing Problem}
\author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
\institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}

\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}
\label{sec:intro}

Firstly, let us introduce the Constrained Ordering Problem:

\begin{definition}
	\label{defn:cop}
	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple. The Constrained Ordering Problem (COP) consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{Z}^{+},$
	\begin{equation}
		\label{eqn:cop}
		\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\},
	\end{equation}
	where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple. The inequality is referred to as the \textup{vicinal sum constraint}.
\end{definition}

@@

One prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \citeauthor{goulimis2004} in 2004. A set $\mathcal{I}$ of rectangular items of equal height $H$ made from cardboard are to be packed onto a strip of height $H$ from left to right. Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places. A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure \ref{fig:boxknife}). However, by design, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry). The distances between each score line and the nearest edge on an item $i \in \mathcal{I}$ are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$, assigned such that $a_i \leq b_i$. Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, or ``rotated'', denoted $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right- hand side of the item respectively. Clearly, for two items to be placed alongside one another feasibly, the sum of the adjacent score widths must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations. Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance. Specifically, as the items are packed from left to right, this involves checking the sum of the right-hand score width of each item $i$ and the left-hand score width of the next item $i+1$ on the strip. The left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.

\begin{figure}[h!]	
	\centering
	\includestandalone[width=0.8\textwidth]{figures/boxesknifeannotate}
	\caption{Width and score widths on an item $i \in \mathcal{I}$, and knives mounted on a bar score two items simultaneously}	
	\label{fig:boxknife}
\end{figure}

@@

\section{Solving the COP}
\label{sec:ahca}

%We shall now present an algorithm for solving the COP, which operates by expressing the problem instance graphically. 
We shall now present an algorithm for solving the COP in polynomial time. The original(underlying) algorithm was created by \cite{becker2010}, and determines whether or not a solution exists for a given instance. We have extended this algorithm so that, if a solution does indeed exist, the algorithm is able to formulate and present us with this final solution. This is especially useful for problems such as the previously mentioned strip-packing problem, where a tangible solution is required in order to place the items in the correct order and orientation. \textcolor{OrangeRed}{USING GRAPH.}

% Equation $v_i + v_j \geq \tau$ provided $p(v_i) \neq v_j$, i.e. not partners
% Bijective function $p: V \to V$ assoc each vertex with its partner, $v_j = p(v_i)$
% Values are assigned from $\mathcal{M}$ in non-decreasing order, i.e. value assoc with v_1 \leq value assoc with v_2 etc..
Let $\mathcal{M}$ be an instance of the COP of cardinality $n$. We model each of the values of all elements in $\mathcal{M}$ as a vertex on a graph $G$, and assign each vertex a value from $\mathcal{M}$ in non-decreasing order. A pair of vertices, called ``dominating vertices'' are then added to the graph, both of which are assigned values equal to $\tau$. These dominating vertices aid the solution process, and are removed at the end. Thus, the graph $G$ has $2n+2$ vertices.

@@

Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$, and two distinct edge sets $B$ and $R$, such that $B \cap R = \emptyset$. Figure \ref{fig:partners/threshold} illustrates the construction of $G$ using the instance $\mathcal{M}$ from the example above.

\begin{figure}	
\centering
\begin{subfigure}[h]{0.45\textwidth}
	\includestandalone[width=\textwidth]{figures/partners}
	\caption{$G = (V, B)$}	
	\label{fig:partners}
\end{subfigure} \hspace{40pt}
\begin{subfigure}[h]{0.45\textwidth}
	\includestandalone[width=\textwidth]{figures/threshold}
	\caption{$G=(V, B \cup R)$}	
	\label{fig:threshold}
\end{subfigure}
\caption{Example construction of $G$ using instance $\mathcal{M}  = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$}
\label{fig:partners/threshold}
\end{figure}

Consider the following definition describing a variant of the classical Hamiltonian cycle on a graph $G$.

\begin{definition}
	\label{defn:althamcycle}
	Let $G(V, B\cup R)$ be an undirected graph, where each edge is a member of one of two sets, $B$ or $R$. $G$ contains an alternating Hamiltonian cycle if there exists a Hamiltonian cycle such that successive edges alternate between sets $B$ and $R$. For example, if $(v_{i-1}, v_i) \in B$, then $(v_i, v_{i+1}) \in R$, or vice versa.
\end{definition}

@@

To find a matching $R' \subseteq R$, the following modified maximum cardinality matching (MMCM) algorithm can be executed, as suggested by \cite{mahadev1994} and \cite{becker2010}: For each vertex $v_i, i=1,2,...,2n+2$, select the edge in $R$ connecting $v_i$ to the highest indexed vertex $v_j$ that is not already incident to an edge in $R'$. Add this edge $(v_i, v_j)$ to $R'$, and proceed to the next vertex until all the vertices have been assessed. The two vertices incident to each matching edge in $R'$ are now referred to as being ``matched''.

During this algorithm, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner $p(v_i)$, the preceeding vertex $v_{i-1}$ can be ``rematched'', provided that 
\begin{enumerate*}[label={(\alph*)}]
	\item $v_i$ is not the first vertex; 
	\item $v_{i-1} \in R'$; and
	\item $(v_{i-1}, p(v_i)) \in R$.
\end{enumerate*}
Then, $v_{i-1}$ is matched with $p(v_i)$, and $v_i$ is matched with the vertex that was previously matched with $v_{i-1}$. It is guaranteed that MMCM will produce a maximum cardinality matching $R' \subseteq R$, and is able to do so in at most $O(n \log n)$ time (\citealp{mahadev1994}).

\begin{figure}	
	\centering
	\begin{subfigure}[h]{0.4\textwidth}
		\includestandalone[width=\textwidth]{figures/matching}
		\caption{$G' = (V, B \cup R')$}	
		\label{fig:matching}
	\end{subfigure} \quad
	\begin{subfigure}[h]{0.5\textwidth}
		\includestandalone[width=\textwidth]{figures/mps}
		\caption{$G' =(V, B \cup R')$ planar}	
		\label{fig:mps}
	\end{subfigure}
	\caption{Spanning subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MMCM algorithm. Planar graph, can see that $G'$ is made up of two components, $q = 2$}
	\label{fig:matching/mps}
\end{figure}

Clearly, if $|R'| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $B$, and hence no feasible solution can be found for the given instance $\mathcal{M}$ of the COP. Otherwise, if $R'$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$ (see Figure \ref{fig:matching/mps}). $G'$ thus consists of a collection of alternating cycles $C_1, C_2, ..., C_q$. In the case where $G'$ comprises one component, i.e. $q = 1$, then this alternating cycle is in fact Hamiltonian, and therefore a feasible solution exists. However, if $q > 1$, the components of $G'$ must be combined to form an alternating Hamiltonian cycle. To do this, a Bridge Recognition (BR) algorithm can be executed that selects suitable edges from $R$ that will replace certain edges in $R'$ in order to function as bridges and connect the components of $G'$.

The edges in $R'$ are sorted into a list such that the lower-indexed vertices of each edge are in increasing order of indices, and the higher-indexed vertices are in decreasing order of indices, i.e. $(v_1, v_{2n+2}), (v_2, v_{2n+1}), ..., (v_{n+1}, v_{n+2})$. Any edges that cannot be placed in such an order are then removed from this list. For instance, in the example illustrated in Figure \ref{fig:matching/mps}, $(v_5, v_9)$ would be removed from the list, since the next edge in the list is $(v_6, v_{10})$, and so the higher-indexed vertices are not in decreasing order. This is due to $v_5$ not being matched with the highest-indexed vertex available, $v_{10}$, during MMCM, as $(v_5, v_{10}) \in B$.

@@

Otherwise, if $k > 1$, it may be that multiple sets are required to connect all components of $G'$. For two sets $R_i$ and $R_j$ to ``overlap'', each set must have one edge from the same component on $G'$, and the other edges in each set must be from different components. For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$, and the other edges in the sets are from different components. Hence, a selection of sets from $R_1, R_2, ..., R_k$ need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the selected sets. If such a collection of sets exists, then the components of $G$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in the collection.

\begin{itemize}
	\item figures explain
\end{itemize}

This algorithm, which will be referred to as the Alternating Hamiltonian Construction Algorithm (AHCA) is able to deduce whether a feasible solution $\mathcal{T}$ exists for any given instance $\mathcal{M}$ of the COP. If a solution does indeed exist, AHCA can produce this solution in at most $O(n^2)$ time.

\begin{figure}	
	\centering
	\begin{subfigure}[H]{0.5\textwidth}
		\includestandalone[width=\textwidth]{figures/mpsconnect}
		\caption{connect}	
		\label{fig:mpsconnect}
	\end{subfigure} \quad
	\begin{subfigure}[H]{0.5\textwidth}
		\includestandalone[width=\textwidth]{figures/mpscycle}
		\caption{cycle}	
		\label{fig:mpscycle}
	\end{subfigure}
	\caption{connect and cycle}
	\label{fig:connect/cycle}
\end{figure}

\begin{theorem}
	\label{thm:copsoln}
	There exists a feasible solution $\mathcal{T}$ to an instance $\mathcal{M}$ of the COP if and only if its corresponding graph $G(V, B\cup R)$ contains an alternating Hamiltonian cycle.
\end{theorem}
\begin{proof}
	Let $\mathcal{A} = \{v_1, v_2, ..., v_{2n+1}, v_{2n+2}\}$ be an alternating Hamiltonian cycle on $G$, where $v_{2n+1}$ and $v_{2n+2}$ are the dominating vertices. By definition, $\mathcal{A}$ contains all vertices on $G$, and all $n+1$ edgs in $B$. Thus, there exists a set of $n+1$ edges from $R$ that, together with the edges in $B$, form the alternating Hamiltonian cycle. Now, removing the dominating vertices and any incident edges gives rise to an alternating Hamiltonian path $\mathcal{A}' = \{v_1, v_2, ..., v_{2n-1}, v_{2n}\}$, whose first edge $(v_1, v_2)$ and last edge $(v_{2n-1}, v_{2n})$ are in $B$. The order of the values corresponding to each vertex of this path form a feasible solution $\mathcal{T}$, where values that are partners make up a tuple. \textcolor{OrangeRed}{edges R vicinal sum constraint equation 2}. \qed
\end{proof}
%put theorem here
%explanation removing dominating vertices
%why is this different from becker

\section{Solving the SCSPP/Heuristics}
\label{sec:scsppsoln}

\begin{itemize}
	\item As mentioned in the introduction, SCSPP is an NP-hard problem, therefore heuristics used
	\item Perhaps the simplest and most well-known heuristics for packing problems is First-Fit (FF), a greedy heuristic/online algorithm that places each item presented in some arbitrary order onto the lowest-indexed strip whose capacity will not be exceeded/such that the capacity of the strip is not exceeded.
	\item It has been shown that there always exists at least one ordering of items such that FF produces an optimal solution (Lewis 2009, General-Purpose HC Method for OIMGP)
	\item A simple modification yields the First-Fit Decreasing (FFD) heuristic, which sorts the items in non-increasing order of size prior to performing FF.
	\item An optimal solution of an instance of the SCSPP is a solution that consists of the fewest number of strips, $k$. A simple lower bound for $k$ that can be computed in $O(n)$ time is given by
	\begin{equation}
	\label{eqn:lowerbound}
	k \geq \ceil*{\frac{\sum_{i=1}^{n}w_i}{W}}
	\end{equation}
	where $n$ is the number of items in the set $\mathcal{I}$, $w_i$ the width of each item $i \in \mathcal{I}$, and $W$ is the width of the strips (\citealp{martello1990b}). In 1973, \citeauthor{johnson1973} showed that FFD is guaranteed to return a solution that uses no more than $\frac{11}{9}k + 4$ strips. More recently, \cite{dosa2007} has proven that the worst case for FFD is in fact $\frac{11}{9}k + \frac{6}{9}$, and that this bound is tight. Due to the initial sorting of the $n$ items in non-increasing order of sizes, the time complexity of FFD is $O(n\log n)$.
	\item However, this bound does not hold for our current problem, as, for example, if $\tau = \infty$, we would require $n$ strips. The value of $\tau$ is not taken into account in the original time complexity.
	\item Difference between BPP and SCSPP: In BPP, an item can be removed from a bin, and feasibility will be retained, however in SCSPP it may not, as the vicinal sum constraint may no longer hold.
	\item Therefore modifications must be made to maintain feasibility.
	\item comparing three heuristics, a basic ffd (basic modification of original FFD), smallest first (Lewis2011) and a heuristic combining FFD and AHCA.
	\item lower bound is also inaccurate, doesn't take into account score widths or $\tau$, very basic lower bound.
	\item feasible candidate solution $\mathcal{S} = \{S_1, S_2,...,S_k\}$ such that
	\item (a) $\bigcup S_i = \mathcal{I}$ (all items in $\mathcal{I}$ packed onto strips)
	\item (b) $S_i \cap S_j = \emptyset$ $\forall i\neq j$ (each item packed onto exactly one strip)
	\item (c) $\forall S_i \in \mathcal{S}$ the items on $S_i$ can be feasibly packed onto a single strip (vicinal sum constraint holds on every strip)
	\item Aim is to minimise $k$.
\end{itemize}

\subsection{FFD Approx}
\label{sec:ffdapprox}
The first heuristic to be discussed is the Score-Constrained First-Fit Decreasing (SCFFD) heuristic, which is an extension of the original FFD. The items in $\mathcal{I}$ are, as usual, sorted in non-increasing order of widths, with ties broken by selecting the item with the smallest score width. Then, for each item $i \in \mathcal{I}$, SCFFD finds the lowest-indexed strip $S_j$ that can accommodate $i$ without being overfilled. If this strip $S_j$ is empty, place $i$ onto $S_j$ in a regular orientation, and add $S_j$ to the solution set $\mathcal{S}$. However, if $S_j$ is not empty, i.e. $S_j \in \mathcal{S}$, the algorithm checks if the vicinal sum constraint is met between the right-most score width on $S_j$ and one of the two score widths on $i$, assessing the smaller score width $a_i$ first. In either case, if the constraint is met, $i$ is placed accordingly onto $S_j$. Indeed, an item $i$ may not fulfil the vicinal sum constraint in any orientation, in which case SCFFD finds the next lowest-indexed strip and attempts to pack $i$ again. This process continues until every item $i \in \mathcal{I}$ has been placed onto a strip $S_j \in \mathcal{S}$. The additional check of the vicinal sum constraints and rotation of the items can be performed in constant time, and as such this heuristic has the same time complexity as FFD, $O(n \log n)$. This heuristic only checks the current items score widths against the right-most score width on a strip, and if the vicinal sum constraint is not met, the item cannot be placed on the strip. However, there may be another location on the strip that the item could be placed in feasibly, or a rearrangement of all items on the strip that produce a feasible alignment.

>>>>

\documentclass[oribibl]{llncs}
\input{includes/preamble.tex}

@@

\title{Heuristics for the Score-Constrained Strip-Packing Problem}
\author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
\institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
\maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}
\label{sec:intro}
Firstly, let us introduce the Constrained Ordering Problem:

\begin{definition}
	\label{defn:cop}
	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple. The Constrained Ordering Problem (COP) consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{Z}^{+},$
	\begin{equation}
		\label{eqn:vsc}
		\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\},
	\end{equation}
	where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple. The inequality is referred to as the \textup{vicinal sum constraint}.
\end{definition}

@@

One prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \citeauthor{goulimis2004} in 2004. A set $\mathcal{I}$ of rectangular items of equal height $H$ made from cardboard are to be packed onto a strip of height $H$ from left to right. Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places. A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure \ref{fig:itemsknife}). However, by design, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry). The distances between each score line and the nearest edge on an item $i \in \mathcal{I}$ are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$, assigned such that $a_i \leq b_i$. Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, or ``rotated'', denoted $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right- hand side of the item respectively. Clearly, for two items to be placed alongside one another feasibly, the sum of the adjacent score widths must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations. Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance. Specifically, as the items are packed from left to right, this involves checking the sum of the right-hand score width of each item $i$ and the left-hand score width of the next item $i+1$ on the strip. The left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.

\begin{figure}[h!]	
	\centering
	\includestandalone[width=0.8\textwidth]{figures/itemsknife}
	\caption{Dimensions of an item $i \in \mathcal{I}$, and knives mounted on a bar score two items simultaneously.}	
	\label{fig:itemsknife}
\end{figure}

@@

\section{Solving the COP}
\label{sec:ahca}
We shall now present an algorithm for solving the COP in polynomial time. The original(underlying) algorithm was created by \cite{becker2010}, and determines whether or not a solution exists for a given instance. We have extended this algorithm so that, if a solution does indeed exist, the algorithm is able to formulate and present us with this final solution. This is especially useful for problems such as the previously mentioned strip-packing problem, where a tangible solution is required in order to place the items in the correct order and orientation.
% We shall now present an algorithm for solving the COP, which operates by expressing the problem instance graphically.

Let $\mathcal{M}$ be an instance of the COP of cardinality $n$. We model each of the values of all elements in $\mathcal{M}$ as a vertex on a graph $G$, and assign each vertex a value from $\mathcal{M}$ in non-decreasing order. A pair of vertices, called ``dominating vertices'' are then added to the graph, both of which are assigned values equal to $\tau$. These dominating vertices aid the solution process, and are removed at the end. Thus, the graph $G$ has $2n+2$ vertices.

@@

Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$, and two distinct edge sets $B$ and $R$ such that $B \cap R = \emptyset$. Figure \ref{fig:partners/threshold} illustrates the construction of $G$ using the instance $\mathcal{M}$ from the example above.
% Equation $v_i + v_j \geq \tau$ provided $p(v_i) \neq v_j$, i.e. not partners
% Bijective function $p: V \to V$ assoc each vertex with its partner, $v_j = p(v_i)$
% Values are assigned from $\mathcal{M}$ in non-decreasing order, i.e. value assoc with v_1 \leq value assoc with v_2 etc..

\begin{figure}	
\centering
\begin{subfigure}[h]{0.45\textwidth}
	\includestandalone[width=\textwidth]{figures/partners}
	\caption{$G = (V, B)$}	
	\label{fig:partners}
\end{subfigure} \hspace{40pt}
\begin{subfigure}[h]{0.45\textwidth}
	\includestandalone[width=\textwidth]{figures/threshold}
	\caption{$G=(V, B \cup R)$}	
	\label{fig:threshold}
\end{subfigure}
\caption{Example construction of $G$ using instance $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$.}
\label{fig:partners/threshold}
\end{figure}

Consider the following definition describing a variant of the classical Hamiltonian cycle on a graph $G$.
\begin{definition}
	\label{defn:althamcycle}
	Let $G(V, B\cup R)$ be an undirected graph, where each edge is a member of one of two sets, $B$ or $R$. $G$ contains an alternating Hamiltonian cycle if there exists a Hamiltonian cycle such that successive edges alternate between sets $B$ and $R$. For example, if $(v_{i-1}, v_i) \in B$, then $(v_i, v_{i+1}) \in R$, or vice versa.
\end{definition}

@@

To find a matching $R' \subseteq R$, the following \textsc{Maximum Cardinality Matching} (MCM) algorithm can be executed, as suggested by \cite{mahadev1994} and \cite{becker2010}: For each vertex $v_i, i=1,2,...,2n+2$, select the edge in $R$ connecting $v_i$ to the highest indexed vertex $v_j$ that is not already incident to an edge in $R'$. Add this edge $(v_i, v_j)$ to $R'$, and proceed to the next vertex until all the vertices have been assessed. The two vertices incident to each matching edge in $R'$ are now referred to as being ``matched''.

During MCM, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner $p(v_i)$, the preceeding vertex $v_{i-1}$ can be ``rematched'', provided that 
\begin{enumerate*}[label={(\alph*)}]
	\item $v_i$ is not the first vertex; 
	\item $v_{i-1} \in R'$; and
	\item $(v_{i-1}, p(v_i)) \in R$.
\end{enumerate*}
Then, $v_{i-1}$ is matched with $p(v_i)$, and $v_i$ is matched with the vertex that was previously matched with $v_{i-1}$. It is guaranteed that MCM will produce a maximum cardinality matching $R' \subseteq R$, and is able to do so in at most $O(n \log n)$ time (\citealp{mahadev1994}).

\begin{figure}	
	\centering
	\begin{subfigure}[h]{0.4\textwidth}
		\includestandalone[width=\textwidth]{figures/matching}
		\caption{$G' = (V, B \cup R')$}	
		\label{fig:matching}
	\end{subfigure} \quad
	\begin{subfigure}[h]{0.5\textwidth}
		\includestandalone[width=\textwidth]{figures/mps}
		\caption{Planar representation of $G' =(V, B \cup R')$}	
		\label{fig:mps}
	\end{subfigure}
	\caption{Spanning subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MCM. The planar representation shows $G'$ comprises $q = 2$ components.}
	\label{fig:matching/mps}
\end{figure}

Clearly, if $|R'| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $B$, and hence no feasible solution can be found for the given instance $\mathcal{M}$ of the COP. Otherwise, if $R'$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$ (see Figure \ref{fig:matching/mps}). $G'$ thus consists of a collection of alternating cycles $C_1, C_2, ..., C_q$. In the case where $G'$ comprises one component, i.e. $q = 1$, then this alternating cycle is in fact Hamiltonian, and therefore a feasible solution exists. However, if $q > 1$, the components of $G'$ must be combined to form an alternating Hamiltonian cycle. To do this, a \textsc{Bridge Recognition} (BR) algorithm can be executed that selects suitable edges from $R$ that will replace certain edges in $R'$ in order to function as bridges and connect the components of $G'$.

The edges in $R'$ are sorted into a list such that the lower-indexed vertices of each edge are in increasing order of indices, and the higher-indexed vertices are in decreasing order of indices, i.e. $(v_1, v_{2n+2}), (v_2, v_{2n+1}), ..., (v_{n+1}, v_{n+2})$. Any edges that cannot be placed in such an order are then removed from this list. For instance, in the example illustrated in Figure \ref{fig:matching/mps}, $(v_5, v_9)$ would be removed from the list, since the next edge in the list is $(v_6, v_{10})$, and so the higher-indexed vertices are not in decreasing order. This is due to $v_5$ not being matched with the highest-indexed vertex available, $v_{10}$, during MCM, as $(v_5, v_{10}) \in B$.

@@

Otherwise, if $k > 1$, it may be that multiple sets are required to connect all components of $G'$. For two sets $R_i$ and $R_j$ to ``overlap'', each set must have one edge from the same component on $G'$, and the other edges in each set must be from different components. For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$, and the other edges in the sets are from different components. Hence, a selection of sets from $R_1, R_2, ..., R_k$ need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the selected sets. If such a collection of sets exists, then the components of $G$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in the collection.
% Refer to figures

This algorithm, which will be referred to as the \textsc{Alternating Hamiltonian Construction Algorithm} (AHCA) is able to deduce whether a feasible solution $\mathcal{T}$ exists for any given instance $\mathcal{M}$ of the COP. If a solution does indeed exist, AHCA can produce this solution in at most $O(n^2)$ time.
% Cite Becker

\begin{figure}	
	\centering
	\begin{subfigure}[H]{0.5\textwidth}
		\includestandalone[width=\textwidth]{figures/mpsconnect}
		\caption{Edges from $R\backslash R'$ can connect vertices from different cycles.}	
		\label{fig:mpsconnect}
	\end{subfigure}
	\begin{subfigure}[H]{0.5\textwidth}
		\includestandalone[width=\textwidth]{figures/mpscycle}
		\caption{Replacing edges connects the components and forms an alternating Hamiltonian cycle.}	
		\label{fig:mpscycle}
	\end{subfigure}
	\caption{Selected edges found using BR can be used to merge the components of $G'$ together, thus forming an alternating Hamiltonian cycle which corresponds to a feasible solution.}
	\label{fig:connect/cycle}
\end{figure}

\begin{theorem}
	\label{thm:copsoln}
	There exists a feasible solution $\mathcal{T}$ to an instance $\mathcal{M}$ of the COP if and only if its corresponding graph $G=(V, B\cup R)$ contains an alternating Hamiltonian cycle.
\end{theorem}
\begin{proof}
	Let $\mathcal{A} = \{v_1, v_2, ..., v_{2n+1}, v_{2n+2}\}$ be an alternating Hamiltonian cycle on $G$, where $v_{2n+1}$ and $v_{2n+2}$ are the dominating vertices. By definition, $\mathcal{A}$ contains all vertices on $G$, and all $n+1$ edgs in $B$. Thus, there exists a set of $n+1$ edges from $R$ that, together with the edges in $B$, form the alternating Hamiltonian cycle. Now, removing the dominating vertices and any incident edges gives rise to an alternating Hamiltonian path $\mathcal{A}' = \{v_1, v_2, ..., v_{2n-1}, v_{2n}\}$, whose first edge $(v_1, v_2)$ and last edge $(v_{2n-1}, v_{2n})$ are in $B$. The order of the values corresponding to each vertex of this path form a feasible solution $\mathcal{T}$, where values that are partners make up a tuple.\qed
\end{proof}

\section{Solving the SCSPP}
\label{sec:scsppsoln}

\begin{definition}
	Let $\mathcal{I}' \subseteq \mathcal{I}$ be a set of items whose total width is less than or equal to the capacity of a strip, (i.e. $\sum_{i=1}^{|\mathcal{I}'|}w_i \leq W$). Given a minimum scoring distance $\tau$, the Score-Constrained Packing Sub-Problem (SCPSP) involves finding an arrangement of the items in $\mathcal{I}'$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
\end{definition}

(Why heuristics, using AHCA for SCSPP, explain) Perhaps the simplest and most well-known heuristic for packing problems is \textsc{First-Fit} (FF), a greedy online algorithm that places each item presented in some arbitrary order onto the lowest-indexed strip such that the capacity of the strip is not exceeded. It is known that there always exists at least one ordering of the items such that FF produces an optimal solution (\citealp{lewis2009}). A minor modification to FF yields the \textsc{First-Fit Decreasing} (FFD) heuristic, which sorts the items in non-increasing order of size prior to performing FF.

For an instance of the SCSPP, a feasible solution is represented by the set $\mathcal{S} = \{S_1, S_2, ..., S_k\}$ such that
\begin{subequations}
	\begin{align}
		\bigcup\nolimits_{j=1}^{|\mathcal{S}|} S_j &= \mathcal{I}, \label{eqn:packall}\\[3pt]
		S_j \cap S_l &= \emptyset \hspace{5mm} \forall \hspace{1mm} j, l \in \{1, 2, ..., |\mathcal{S}|\}, \hspace{2mm} j \neq l, \label{eqn:nooverlap} \\[3pt]
		\sum\nolimits_{i=1}^{|S_j|}w_i & \leq W \hspace{3mm} \forall \hspace{1mm} S_j \in \mathcal{S}, \label{eqn:capacity} \\[3pt]
		\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) &\geq \tau \hspace {5mm} \forall \hspace{1mm} i \in \{1, 2, ..., |S_j|-1\}, \hspace{2mm} \forall \hspace{1mm} S_j \in \mathcal{S}. \label{eqn:vscstrip}
\end{align}
\end{subequations}

That is, all items must be packed onto a strip, each item can only be placed on one strip, the strips cannot be overpacked, and the items on each strip $S_j$ in the solution must be arranged such that the sum of two adjacent score widths is greater than or equal to the minimum scoring distance $\tau$.

An optimal solution $\mathcal{S}$ of an instance of the SCSPP is a solution that consists of the fewest number of strips $k$. A simple lower bound for $k$ that can be computed in $O(n)$ time is given by 
\begin{equation}
\label{eqn:lowerbound}
k \geq \ceil*{\frac{\sum_{i=1}^{n}w_i}{W}},
\end{equation}
where $n$ is the number of items ($|\mathcal{I}|$), $w_i$ the width of each item $i \in \mathcal{I}$, and $W$ is the width of the strips (\citealp{martello1990b}). In 1973, \citeauthor{johnson1973} showed that FFD is guaranteed to return a solution that uses no more than $\frac{11}{9}k + 4$ strips. More recently, \cite{dosa2007} has proven that the worst case for FFD is in fact $\frac{11}{9}k + \frac{6}{9}$, and that this bound is tight. Due to the initial sorting of the $n$ items in non-increasing order of sizes, the time complexity of FFD is $O(n\log n)$.

As mentioned in the introduction, the SCSPP shares many similarities with the BPP, however the addition of constraint (\ref{eqn:vscstrip}) induces complications that must be taken into consideration. One obvious difference is the order in which the items must appear on the strips. In the BPP, removing an item retains feasibility, whereas in the SCSPP this is not guaranteed, as the constraint may not be fulfilled between the two score widths either side of the item removed. Furthermore, lower bound for $k$ (Equation (\ref{eqn:lowerbound})) does not hold for the SCSPP, as the minimum scoring distance $\tau$ is not included in the calculation. For example, if $\tau > 2 \max(b_i)$ (that is, the minimum scoring distance is greater than twice the largest score width), then it is clear that $n$ strips will be required, regardless of the items' widths.
% Time complexity for FFD also inaccurate

Three heuristics for the SCSPP have been developed: a basic FFD heuristic with a simple modification; a heuristic that packs strips individually and prioritises score widths; and a powerful version of FFD that incorporates the polynomial-time AHCA algorithm.

\subsection{Modified First-Fit Decreasing Heuristic (MFFD)}
\label{sec:mffd}
The \textsc{Modified First-Fit Decreasing} (MFFD) heuristic performs in the same manner as the original FFD, attempting to place each item onto the end of the lowest-indexed strip. If an item is able to be packed onto a strip without exceeding the strip's capacity, MFFD then checks to see if the vicinal sum constraint is met between the right-most score on the strip and one of the score widths on the current item. If the constraint is met, MFFD places the item on the end of the strip in the appropriate orientation, else the heuristic attempts to pack the item onto the next lowest-indexed strip. For example, in Figure \ref{fig:comparestrips}, the strip is able to accommodate the current item, however the vicinal sum constraint is not fulfilled regardless of the orientation of the item, and therefore the item cannot be feasibly packed onto the strip.
